### 2025-01-15 reviewer-response.md

*The Results section is a slog to read and parts of the Discussion seem
redundant.  Take lines 651 to 668 as an example.  Tightening up the
Results and the Discussion can only help the exposition.*

offload to figure captions where possible, don't spell out everything

*I led a bioinformatics project that used an entropy scaling approach to
search a database of protein sequences.  See Reference [1].  As a result,
I am confused about some of the real world examples.  I know that protein
sequences are challenging to search for reasons such as their having
widely varying lengths and there being no obvious notion of a center of a
set of protein sequences.  In any case, I would like the authors to
reference [1] and discuss in more depth how they address the challenges of
the various real world examples.*

The fact that protein sequences have widely varying lengths does pose problems in terms of the potential sparsity of the manifold; it suggests that many distances would be maximized. While this makes the notion of a 'center' somewhat arbitrary and meaningless in domain terms, there would still be a computable cluster center (as demonstrated in work we just published in IEEE Big Data, largely done after the CAKES work). However, the approach in [1] is quite justified. We have added a discussion of protein sequence search as a specific example of a difficult domain, and cited [1] among others.

### 2025-01-15 sections/5-discussion.tex
discussion of protein sequence search

>>>>

We note that despite the genericity of CAKES, effectively applying it to real-world datasets may typically require domain-specific knowledge. As an example, consider the domain of protein sequence search; protein sequences are of highly variable length (30--1000 amino acids are typical, with some outliers) and typically comprise a 20-letter alphabet. There have been numerous protein sequence search algorithms~\cite{kim2021entrance, daniels2013compressive, yu2015entropy, steinegger2018clustering}, and the one thing they have in common besides the application domain is that their development required deep domain-specific knowledge. While simple edit distance may be a poor choice for clustering when sequence lengths exhibit such variance, other choices of distance metrics and preprocessing could be used by CAKES, such as representing each sequence as a set of $k$-mers (short substrings of length $k$) and choosing Jaccard distance as the metric; this approach was chosen by~\cite{kim2021entrance}.
